Long-range Interatomic Coulombic Decay in ArXe clusters: Experiment and Theory

### 2016-08-08 letters/reply_referee.tex

  \item \emph{Page 18:
        it is stated that the decay width decreases like R-6 but in page 20 it decreases exponentially.}\\
        The reason is that it discusses different interatomic distances being
        the energy transfer distance $R$ ($R^{-6}$) and the electron
        transfer distance $Q$ ($e^{-Q}$) which can both be found in previous and
        coming papers about ETMD(3) (J. Chem. Phys. \textbf{138}, 014305 (2013).
        and Fasshauer \emph{et al.} Mol. Phys. (2016), submitted.):
\begin{center}
 \includegraphics[width=6cm]{../pics/coord_systems.pdf}
\end{center}
        Both on page 18 and 20, these distances are very clearly characterized
        in terms involved atom types or groups and which process is ongoing.
        To further clarify the matter, the sentences on page 18 now read:\\
        Two aspects have to be taken into account: an energy shift of the peaks
        due to different charge distances {\color{blue}{$d$}} in the
        final state (i.e. the interatomic Xe-Xe
        distance) and the decrease of the decay width with $R^{-6}$,
        $R$ being the distance between the electron transfer unit and the xenon
        atom ionized in the final state.
        The larger the distance between the xenon atoms, the higher are the
        energies of the secondary electrons{\color{blue}{. For the case of xenon
        atoms on argon surfaces this at the same time means a larger distance
        between the Ar-Xe pair involved in the electron transfer and the
        electron emitting xenon atom. Hence, the decay widths are smaller.}}
        Therefore, a
        significant contribution from ETMD(3) compared to ICD is only
        seen if the two xenon atoms reside on two adjacent
        surfaces.

  \item \emph{Page 29:
        the efficiency of ICD is found below unity for clusters having few Xe atoms. I guess this is because in these clusters ICD and ETMD are closed for some Argon atoms which are anyway ionized. Maybe a statistical model may explain it. The theory could also help since it should be easy to determine the efficiency for all clusters considered in this study.}\vspace{0.3cm}\\
        This is a good point from the referee. We have included a short discussion of the possible explanations of this effect at the respective place: {\color{blue}{Two main reasons can be identified that cause a decrease in autoionization efficiency. First, is the distance between the initially ionized Ar atom to the decay partner too large, then the excited Ar ion can decay via fluorescence before it can autoionize. And second, if there is no decay partner available at a sufficiently large distance, then a decay is energetically not possible. In both cases, a small Xe content would lead to a decrease in autoionization efficiency. The first case should not occur in small clusters while the second should strongly increase with decreasing cluster size. }}

### 2016-08-08 letters/reply_referee.tex

\textbf{Referee \#1} raised the following points:

\begin{enumerate}
 \item \emph{In general, I find the manuscript clearly written but unnecessary long. Some details and discussions can be avoided without weakening the presentation. Here are some examples:}
  \begin{enumerate}
   \item \emph{ICD is explained twice in the introduction (top of page 3 and
         3rd paragraph of page 3)}\\

				We have deleted the explanation of ICD in the 3rd paragraph of page 3.

   \item \emph{the sentence: The notion of ICD requires that the electronic orbitals … can be distinguished... make a distinction between ICD and Auger decay. does not bring important informations. Furthermore, using only a one-particle picture to define ICD may be misleading. For example, in molecular clusters ICD can be clearly identified after deep ionization (typically for binding energy above 20 eV) of one molecule. However, owing to the strong electronic correlation in this binding energy range the states cannot be described as ionization from a single orbital.}\\\vspace{0.3cm}\\
				The referee is correct, the statement does not bring new information. We have therefore deleted this section from the manuscript. That is also in accordance to the referees notion that the manuscript is too long.

	\item \emph{Page 9: the sentence “These atoms do not necessarily need to form bonds...” just rephrases what is already explained earlier in the manuscript on ICD.}\vspace{0.3cm}\\
         The comment skips the important part of the argumentation, which is
         that the units/atoms do not need to be close. The comment about the
         bonding situation was made intentionally to clarify the difference
         between pairs and triples on the one hand and dimers and trimers on
         the other hand. We therefore do not change the sentence.

@@

   \item \emph{Page 10: the definition of open and close channel is repeated. Explanations in page 9 and figure 1 are enough.}\vspace{0.3cm}\\
         The explanation on page 10 belongs to the explanation on page 9, which
         would not be understandable without half of the text. While the
         text formulates the general concept, the figure illustrates this concept
         on an example which is this manuscript's system under investigation.
         Since also the caption of the figure should be understandable without
         reading the text, we do not shorten the manuscript at this point.

   \item \emph{Page 13:
         the section “Cluster Structures” can be moved to Supporting information since only Table 2 is important to understand the results. Furthermore, it seems to me that the paragraph on previous study of the authors on large clusters does provide relevant informations on the reported results.}\vspace{0.3cm}\\

     The whole section consists of only four paragraphs in total and is rather short. The cluster structures are crucial for understanding the underlying theory and results. It is a very descriptive part of the manuscript and helps the reader to assess the different structures and classes under discussion. We therefore think that it will not improve the MS if the whole section is moved to the supplementary information. (note that a large part of this section is already there).

   \item \emph{Page:
         the section Outer valence spectra is very detailed and the reader may lose the main point of this section which is, as far as I understood, to evaluate experimentally the percentage of Xe in the clusters. All extra details can be avoided. Just to help the readers, this section could be renamed to highlight the goal of the section like for example “Xe content”.}\vspace{0.3cm}\\
				The referee is correct if one reads the article from a theoreticians point of view. However, the outer valence spectra of our clusters were not reported in this detail earlier nor were they ever discussed. We therefore think that this section holds very valuable information for the experimentalist which we do not want to hide in the supplementary section. To accommodate the referees suggestion we have included two sentences in the beginning of the section, summarizing the points that are most important for the theory part of the article: {\color{blue}{This section describes and discusses the outer valence spectra of the mixed Ar-Xe clusters. The main information we obtain from these spectra within the context of our theoretical considerations are
the single ionization potentials and
the relative Xe contents in the mixed cluster.}}

@@

\end{enumerate}

\textbf{Referee \#2} raised the following points:

\begin{enumerate}
 \item \emph{ETMD(3) should be explained in the introduction by a sentence or two to aid the reader (at the moment, it is first explained in the theory section).
}\vspace{0.3cm}\\
       It was indeed explained already but in wording specific to
       experimentalists. We therefore changed the last paragraph on page 3 to:\\
       Soon after, related autoionization processes were discovered
       {\color{blue}{in which the initial vacancy is filled by an electron from a neighbouring unit. These were termed `Electron Transfer Mediated Decay'
(ETMD)$^{9–12}$. If the excess energy is transferred to a third unit which is subsequently ionized, the process is called ETMD(3), if the electron donor is ionized once more the process is called ETMD(2) and if the excess energy is used to ionize the initially ionized unit the process is called `exchange ICD'$^{13,14}.$}}

 \item \emph{The authors mention that the ‘nuclear dynamics may play an important role’ but that they have been neglected in the calculations. While I understand that it is not feasible in such large systems the authors should at least briefly discuss the possible effect of nuclear dynamics e.g. peak shifts, broadening, ICD vs. ETMD, etc. }\vspace{0.3cm}\\
       We added two paragraphs at the end of the theoretical results section
       discussing the possible effects of nuclear dynamics:\\
       {\color{blue}{All these results neglect the effect of nuclear dynamics, which might affect the spectra. Possible reasons are distance dependent channel closings and openings, a different distribution of interatomic distances due to vibrations and their different impact on the ICD and the ETMD(3). E.g., for the ICD in the neon dimer, the treatment of nuclear dynamics increases the decay width by approximately a factor 2.$^{57}$ However, the atomic displacement can be expected to be far less severe in clusters than in dimers or trimers. Additionally, the
elongation of one interatomic distance in a cluster automatically results in the shortening of a different interatomic distance, which will reduce the overall effect. Therefore, there will be a broader spectrum charges in the final state d resulting in a broadening of the peak. This was taken into account by folding the stick spectrum with Gaussians with a width of 300 meV and 600 meV for the ICD and ETMD(3), respectively. While the width of the ICD peaks was estimated from the potential energy surface of the ArXe dimer, the situation is more complex in case of the ETMD(3) with three degrees of freedom involved. It was therefore guessed to be twice the width of the ICD peak.
The channel closing due to shortening of the interatomic distance is not relevant for the ETMD(3) process in the ArXe clusters, treated in this work, because this would require unnaturally short interatomic distances. However, for the ICD it might result in a lower number of pairs with open decay channels and hence decrease the decay width. Since the folded peaks are constituted from several pairs of different distances, it would result in a slight peak shift to higher energies of the combined peak at lowest energy. For a more detailed discussion of nuclear dynamics for the ICD in dimers vs. in clusters see Ref 58.}}

### 2016-08-12 exp_results.tex

We found an Ar 3s autoionization efficiency which, for clusters with the lowest Xe content (Xe$_{\rm cl}$ approx. 10-12\,\%), is smaller than unity, and further decreases with decreasing cluster size.

In clusters with a low Xe content we can assume that there are Ar atoms that have distances to the next Xe atom that are too large for autoionization to occur. This is especially the case if we have very large clusters that show segregation of Ar and Xe atoms. If we decrease the cluster size, this effect should play a minor role because large distances are not available here. However, with decreasing cluster size, the number of homogeneous clusters in the cluster beam increases. In fact, at small cluster sizes, the size distribution has its maximum at the monomer. This increasing number of homogeneous Ar clusters still show Ar 3s intensity but do not contribute to recorded coincidences because they cannot autoionize. For larger Xe$_{\rm cl}$, the values are compatible with unity, within the accuracy of our experiment.

>>>>

We found an Ar 3s autoionization efficiency which, for clusters with the lowest Xe content (Xe$_{\rm cl}$ approx. 10-12\,\%), is smaller than unity, and further decreases with decreasing cluster size. Two main reasons can be identified that cause this decrease in autoionization efficiency. First, is the distance between the initially ionized Ar atom to the decay partner too large, then the excited Ar ion can decay via fluorescence before it can autoionize. And second, if there is no decay partner available at a sufficiently large distance, then a decay is energetically not possible. In both cases, a small Xe content would lead to a decrease in autoionization efficiency. The first case should not occur in small clusters while the second should strongly increase with decreasing cluster size. For larger Xe$_{\rm cl}$, the values are compatible with unity, within the accuracy of our experiment.

### 2016-08-12 theo_results.tex

All these results neglect the effect of nuclear dynamics, which might
affect the spectra. Possible reasons are distance dependend channel closings
and openings,
a different distribution of interatomic distances due to vibrations
and their different impact on
the ICD and the ETMD(3). E.g., for the ICD in the neon dimer, the treatment of
nuclear dynamics increases the decay width by approximately a factor 2
\cite{Schnorr15}.
However, the atomic displacement can be expected to be by far less severe
in clusters than in dimers or trimers. Additionally, 
the elongation of one interatomic distance in a cluster
automatically results in
the shortening of a different interatomic distance, which will reduce
the overall effect. Therefore, there will be a broader spectrum charges in the
final state $d$ resulting in a broadening of the peak. This was taken into
account by folding the stick spectrum with Gaussians with a width of
\unit[300]{meV} and \unit[600]{meV} for the ICD and ETMD(3), respectively.
While the width of the ICD peaks was estimated from the potential energy
surface of the ArXe dimer, the situation is more complex in case of the ETMD(3)
with three degrees of freedom involved. It was therefore guessed to be twice the
width of the ICD peak.

The channel closing due to shortening of the interatomic distance is not
relevant for the ETMD(3) process in the ArXe clusters, treated in this work,
because this would require unnaturally short interatomic distances.
However, for the ICD it might result in a lower number of pairs with open
decay channels and hence decrease the decay width. Since the folded peaks
are constituted from several pairs of different distances, it would result
in a slight peak shift to higher energies of the combined peak at lowest energy.
For a more detailed discussion of nculear dynamics for the ICD in dimers vs.
in clusters see Ref. \citenum{fasshauernjp}

>>>>

All these results neglect the effect of nuclear dynamics, which might
affect the spectra. Possible reasons are distance dependent channel closings
and openings,
a different distribution of interatomic distances due to vibrations
and their different impact on
the ICD and the ETMD(3). E.g., for the ICD in the neon dimer, the treatment of
nuclear dynamics increases the decay width by approximately a factor 2
\cite{Schnorr15}.
However, the atomic displacement can be expected to be far less severe
in clusters than in dimers or trimers. Additionally, 
the elongation of one interatomic distance in a cluster
automatically results in
the shortening of a different interatomic distance, which will reduce
the overall effect. Therefore, there will be a broader spectrum charges in the
final state $d$ resulting in a broadening of the peak. This was taken into
account by folding the stick spectrum with Gaussians with a width of
\unit[300]{meV} and \unit[600]{meV} for the ICD and ETMD(3), respectively.
While the width of the ICD peaks was estimated from the potential energy
surface of the ArXe dimer, the situation is more complex in case of the ETMD(3)
with three degrees of freedom involved. It was therefore guessed to be twice the
width of the ICD peak.

The channel closing due to shortening of the interatomic distance is not
relevant for the ETMD(3) process in the ArXe clusters, treated in this work,
because this would require unnaturally short interatomic distances.
However, for the ICD it might result in a lower number of pairs with open
decay channels and hence decrease the decay width. Since the folded peaks
are constituted from several pairs of different distances, it would result
in a slight peak shift to higher energies of the combined peak at lowest energy.
For a more detailed discussion of nuclear dynamics for the ICD in dimers vs.
in clusters see Ref. \citenum{fasshauernjp}
